KidsAIR: exposure model

### 2020-05-20 exposure_covariate_associations.Rmd
minor exposure analysis updates

  analysis_results <- lm(log(pm_mean_sampling_period) ~ analysis_covar, analysis_data)

  tidy_results <<- tidy(analysis_results, conf.int = TRUE) %>% 
    filter(term != '(Intercept)') %>% 
    mutate(Estimate = round(estimate, digits = 2),
           'P-value' = round(p.value, digits = 2),
           'Upper 95% CL' = round(conf.high, digits = 2),
           'Lower 95% CL' = round(conf.low, digits = 2),
           Term = gsub("analysis_covar", paste0(label, ": "), term)) %>% 
    select(Term, Estimate, 'Lower 95% CL', 'Upper 95% CL', 'P-value')

>>>>

  analysis_results <<- lm(log(pm_mean_sampling_period) ~ analysis_covar, analysis_data)

  tidy_results <<- tidy(analysis_results, conf.int = TRUE) %>% 
    filter(term != '(Intercept)') %>% 
    mutate(Estimate = round((exp(estimate)-1)*100, digits = 2),
           'P-value' = round(p.value, digits = 2),
           'Upper 95% CL' = round((exp(conf.high)-1)*100, digits = 2),
           'Lower 95% CL' = round((exp(conf.low)-1)*100, digits = 2),
           Term = gsub("analysis_covar", paste0(label, ": "), term)) %>% 
    select(Term, Estimate, 'Lower 95% CL', 'Upper 95% CL', 'P-value')

### 2020-05-20 exposure_models.Rmd
minor exposure analysis updates

print(exposure_model)
```

>>>>

print(exposure_model)

# Exponentiate results for manuscript tables
exp_results <- as.data.frame(exposure_model$coefficients.s) %>% 
  rownames_to_column() %>% 
  mutate(estimate = round((exp(Estimate)-1)*100, digits = 2),
         ci_low = round((exp(`Lower CI`)-1)*100, digits = 2),
         ci_hi = round((exp(`Upper CI`)-1)*100, digits = 2)) %>% 
  select(rowname, estimate, ci_low, ci_hi)

exp_results
```
